Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-07 paper.tex
baseline data for symbolic regression
symbolic regression data

\begin{table}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  98\% solved&94\% \\
  $2.71\pm 0.07$ sec& $2.84\pm0.07$
  \\\bottomrule
\end{tabular}\caption{\% held out tasks solved and average solve time for symbolic regression}\label{regressionComparison}
\end{table}

>>>>

\begin{table}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  98\% solved&94\%&0.7\%&0\%&2\% \\
  $2.71$ sec& $2.84$  &$3.6$ sec&--&\\
  $9.3$ nats &$11$ nats&$2.3$ nats&--&$4.6$ nats
  \\\bottomrule
\end{tabular}\caption{Symbolic regression. Top: \% held out tasks solved w/ 5 second timeout. Middle: average solve time. Bottom: average description length $-\log \probability[x|p]$. ``No NN'' solves almost as many tasks but
using worse programs w/ extraneous degrees of freedom, increasing  description length.}\label{regressionComparison}
\end{table}
